---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Quick start

Welcome to the `caress` GitHub page!

Neural networks have lots of applications. A lot of people want to learn how to use them. The keras package makes it easy to design neural network architectures. The caress package makes it even easier.

```{r, eval = FALSE}
library(devtools)
devtools::install_github("tpq/caress")
```

This package includes some helper functions that automate bread-and-butter network building. For example, they one-hot encode factors, normalize the feature input, set the input size, set the output size, and choose the correct loss function. I also wanted to make the functional API easier to use by going `from_input` on `to_output`.

```{r}
library(keras)
library(caress)
data(iris)
data <- sample_random(x = iris[,1:4], y = iris[,5], split = 80, normalize = TRUE)
x_train <- data$train$x
y_train <- data$train$y
x_test <- data$test$x
y_test <- data$test$y

input <- from_input(x_train)
output <- input %>%
  layer_dense(units = 2, activation = "tanh") %>%
  to_output(y_train)

model <- prepare(input, output)
```

Now, we can compile and fit the model with a single function call.

```{r, eval = FALSE}
history <- build(model, x_train, y_train, epochs = 100, batch_size = 8)
evaluate(model, x_test, y_test)
```

## Multiple Inputs and Outputs

The `from_input` and `to_output` functions will accept lists of objects. In this case, these functions return a list of layers that you can pass through the functional API to create complex multi-input and multi-output network architectures.

```{r}
data(iris)
data <- sample_random(x = iris[,1:4], y = iris[,5], split = 80, normalize = TRUE)
x_train <- data$train$x[,1:3]
y_train <- data$train$y
z_train <- data$train$x[,4]

inputs <- from_input(list(x_train, z_train))
channel1 <- inputs[[1]] %>%
  layer_dense(units = 2, activation = "tanh") %>%
  to_output(list(y_train, z_train), name = "output_mixed")
channel2 <- layer_concatenate(list(inputs[[2]], channel1[[2]])) %>%
  layer_dense(units = 2, activation = "tanh") %>%
  to_output(y_train, name = "output_final")
  
model <- prepare(inputs, list(channel1[[1]], channel2))
```

Use a named list to supply all inputs and outputs to the `build` module.

```{r, eval = FALSE}
build(model,
      list("input_1" = x_train, "input_2" = z_train),
      list("output_mixed_1" = y_train, "output_final" = y_train))
```
